О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-27 pps-linear-bound/pps-linear-lower-bound.tex
Proofreading by Usachev - p. 13

\begin{remark}
	The bound of Theorem~\ref{thm:main_estimate} is not tight.
	The derivation of tight bounds for the minimum diameter $d(2, n)$
	is still a challenging task for the future~\cite[Section 7]{kurz2008minimum}.
\end{remark}
The known upper bound is $d(2,n)\leq 2^{c \log n \log \log n}$~\cite{harborth1993upper}.
However, we hope that the present article can give a framework for future better estimates.

@@

There are also the following ways to improve the current bound,
based on Lemma~\ref{lem:square_container}.

\begin{problem}
	\label{prb:square_side_length_and_diameter_power}
	Is there a number $\delta < 1$ such that any $M\in\mathfrak{M}(2,\mathbb{N})$ with $\operatorname{diam} M = d$
	is situated in a square of side length $d^\delta$?
\end{problem}
If the answer for Problem~\ref{prb:square_side_length_and_diameter_power} is affirmative,
then we can build a bound better than linear.

>>>>

\begin{remark}
	The bound of Theorem~\ref{thm:main_estimate} is not tight.
	The derivation of tight bounds for the minimum diameter $d(2, n)$
	is still a challenging task for the forthcoming investigation~\cite[Section 7]{kurz2008minimum}.
\end{remark}
The known upper bound is $d(2,n)\leq 2^{c \log n \log \log n}$~\cite{harborth1993upper}.
However, we hope that the present article can provide a framework for possible better estimates.

@@

There are also several ways to improve the current bound,
based on Lemma~\ref{lem:square_container}.

\begin{problem}
	\label{prb:square_side_length_and_diameter_power}
	Is there a number $\delta < 1$ such that any $M\in\mathfrak{M}(2,\mathbb{N})$ with $\operatorname{diam} M = d$
	is situated in a square of side length $d^\delta$?
\end{problem}
If the answer for Problem~\ref{prb:square_side_length_and_diameter_power} is affirmative,
then we can obtain a bound better than linear.
